\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-06-25 coqimpl.tex
Reply the comments

Once the user closes a family with "EndFamily", they can access its fields by using module syntax. For example, they can access "A.a" to get "1" after "Family A" is defined. This is achieved by a complete compilation from a family to a module, via aggregating the list of the modules in the internal representation: the plugin will repeatedly using Coq's "Include" command as the "Module A" in \cref{fig:plugin-example1} illustrates. Now, the user can use "Module A" anywhere as they are using "Family A".
\YZ{The reader wonders why this aggregation is needed. 
Seems like the place to talk about how the programmer can use A outside Family A.}

@@

Inherits Until MonotonicF.
Override Family MonotonicF.
  Final Field f : nat@\YZ{nat -> nat ?}@ := (+ 1).

  Field p : monotonic f := ...
 SealFamily. 
EndFamily.
\end{minted}
  \end{minipage}
  \caption{Example Code for Inheritance and Reasoning}\label{fig:plugin-example3}
\end{figure}

@@

Since it is possible to consider inheritance as solely a first-order data rather
than a higher-order functor, it is possible to
\text{mix-in} two inheritance data---by carefully ``mix'' the internal list.\YZ{How about making mixin composition one of your Req's? Also does any example in the paper illustrate how to do this?}

@@

In our Coq plugin, we can achieve such exposure of definitional equality by
exposing the whole definition directly into the compiled module type. Doing so we also prohibit overriding because
subtraction doesn't have the same definition as $add$. We require the
users to decorate field as `Final' so that the plugin will proceed with
this special treatment.\YZ{This para is confusing: which kind of equality is used, propositional or judgmental? Where does 'Final' show up in the example?}\EDJreply{I rephrase it and remove the part on taking about meta-theory. Now everything is about judgemental so I don't have to emphasize judgemental. I wanted to make the example small but I guess I can add one `Final' statement into our example. Don't resolve it until I add it into Figure 2.}

@@

To resolve this, we provide family sealing mechanism to simulate sigma type---we allow the
users to specify the compiled module type of a given family, and thus we
can have a \textit{non-overridable} (thus locally transparent) field
located in an \textit{overridable} family.
See, for example, the "MonotonicF" in \cref{fig:plugin-example3}.
We simply seal
\mintinline{Coq}{f : nat → nat} and \mintinline{Coq}{p : monotonic f}
together inside an overridable family that does not allow "f"
to be overridden in any of its derived families.
Because "f" is non-overridable inside the family, its definition is
transparent and can be used to prove "p".
However, because the enclosing family of "f" is overridable, to swap the
implementation of "f", we just override the whole ``sealed'' family,
like we do in "I2.MonotonicF". And the compiled module type of
"MonotonicF" will be fixed throughout the extension in different
families---it is always these two fields "f, p".\YZ{Can an overriding, sealed family define new fields not in its parent?}

>>>>

Once the user closes a family with "EndFamily", they can access its fields by using module syntax. For example, they can access "A.a" to get "1" after "Family A" is defined. This is achieved by a complete compilation from a family to a module, via aggregating the list of the modules in the internal representation: the plugin will repeatedly using Coq's "Include" command as the "Module A" in \cref{fig:plugin-example1} illustrates. Now, the user can use "Module A" anywhere as they are using "Family A".
\YZ{The reader wonders why this aggregation is needed. 
Seems like the place to talk about how the programmer can use A outside Family A.}\EDJreply{Please check.}

@@

Inherits Until MonotonicF.
Override Family MonotonicF.
  Final Field f : nat -> nat@\YZ{nat -> nat ?}\EDJreply{Yes. Thanks}@ := (+ 1).
  Field p : monotonic f := ...
 EndFamily. 
EndFamily.
\end{minted}
  \end{minipage}
  \caption{Example Code for Inheritance and Reasoning}\label{fig:plugin-example3}
\end{figure}

@@

Since it is possible to consider inheritance as solely a first-order data rather
than a higher-order functor, it is possible to
\text{mix-in} two inheritance data---by carefully ``mix'' the internal list.However, a good definition of mixin is still under investigation.\YZ{How about making mixin composition one of your Req's? Also does any example in the paper illustrate how to do this?}\EDJreply{mixin is not really formalized. There is no example illustrate it. The only example is the STLC example at the very end and I just kind of ``mention'' it. I think here I just want to emphasize, inheritance as first order data is still possible to support composition.}

@@

In our Coq plugin, we can achieve such exposure of definitional equality by
exposing the whole definition directly into the compiled module type. Doing so we also prohibit overriding because
subtraction doesn't have the same definition as $add$. We require the
users to decorate field as `Final' so that the plugin will proceed with
this special treatment.\YZ{This para is confusing: which kind of equality is used, propositional or judgmental? Where does 'Final' show up in the example?}\EDJreply{I rephrase it and remove the part on talking about meta-theory. Now everything is about judgemental so I don't have to emphasize judgemental. I wanted to make the example small but I guess I can add one `Final' statement into our example. Don't resolve it until I add it into Figure 2.}

@@

To resolve this, we provide family sealing mechanism to simulate sigma type---we allow the
users to specify the compiled module type of a given family, and thus we
can have a \textit{non-overridable} (thus locally transparent) field
located in an \textit{overridable} family.
See, for example, the "MonotonicF" in \cref{fig:plugin-example3}.
We simply seal
\mintinline{Coq}{f : nat → nat} and \mintinline{Coq}{p : monotonic f}
together inside an overridable family that does not allow "f"
to be overridden in any of its derived families.
Because "f" is non-overridable inside the family, its definition is
transparent and can be used to prove "p".
However, because the enclosing family of "f" is overridable, to swap the
implementation of "f", we just override the whole ``sealed'' family,
like we do in "I2.MonotonicF". And the compiled module type of
"MonotonicF" will be fixed throughout the extension in different
families---it is always these two fields "f, p".\YZ{Can an overriding, sealed family define new fields not in its parent?}\EDJreply{I don't find this a problem but I didn't support it in my plugin. }
